Screening and coding with LLMs

### 2024-10-23 LLMs/pres/LLM-screening_wed_seminar.tex

\title[Chatbots Annotators]{LLM-prioritised screening}

@@

\section{Introduction}

\section{Implementation}

@@

\section{Results}

@@

\section{Conclusion}

@@

\begin{frame}{Conclusions}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item<1-> LLMs are neither a quick fix or a silver bullet
				\item<2-> Evaluation is vital
				\item<3-> We can't forget the need for appropriate stopping criteria \cite{callaghan_statistical_2020}
				\item<4->\url{mcallaghan.github.io/buscar-app}
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\only<3>{\includegraphics[width=\columnwidth]{../../figures/stopping.pdf}}
			\end{figure}
		\end{column}
	\end{columns}

@@

\begin{frame}
	Thanks!

	\bigskip

	\hrule

	\bigskip

	\url{callaghan@mcc-berlin.net}

	\medskip

	Twitter: @MaxCallaghan5

	\bigskip

	\begin{figure}
	\includegraphics[width=0.1\columnwidth]{images/wellcome-logo-black.eps}
	\end{figure}
\end{frame}

>>>>

\title[LLM screening and coding]{Screening and coding with LLMs}

@@

\begin{frame}{Outlook}
	\begin{itemize}
		\item<1-> Results from the implementation of \cite{wang_zero-shot_2024}
		\item<2-> Additional results from Santiago's thesis project on coding
	\end{itemize}
\end{frame}

%\section{Introduction}
%
%\section{Implementation}

\section{Screening}

@@

%\section{Results}

@@

%\section{Conclusion}

@@

\begin{frame}{Conclusions}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item<1-> LLMs are neither a quick fix or a silver bullet
				\item<2-> Evaluation is vital
				\item<3-> We can't forget the need for appropriate stopping criteria \cite{callaghan_statistical_2020}
				%\item<4->\url{mcallaghan.github.io/buscar-app}
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\only<3>{\includegraphics[width=\columnwidth]{../../figures/stopping.pdf}}
			\end{figure}
		\end{column}
	\end{columns}

@@

\section{Coding}

\begin{frame}{Using LLMs for coding}
		\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item<1-> Santiago's thesis showed us that LLMs can achieve comparable performance with BERT-type models
				\item<2->They need no training data to achieve this performance
				\item<3->But we do need annotated data for ``prompt engineering'' ($\approx$ training?), and for evaluation
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\only<1->{\includegraphics[width=\columnwidth]{../../figures/LLM-coding.pdf}}
			\end{figure}
		\end{column}
	\end{columns}

\begin{frame}{Using LLMs for coding}
	\begin{columns}
		\begin{column}{0.4\linewidth}
			\begin{itemize}
				\item<1-> Results were aggregated Macro F1 scores for 30 labels
				\item<2-> Aggregate results hide much variation
				\item<3-> This varies across the different coding categories
				\item<4-> And there seems to be a clear correlation with number of labels
			\end{itemize}
		\end{column}
		\begin{column}{0.6\linewidth}
			\begin{figure}
				\only<2>{\includegraphics[width=\columnwidth]{../../../LLM-eval/gpt/figures/BERT-vs-LLMs.pdf}}
				\only<3>{\includegraphics[width=\columnwidth]{../../../LLM-eval/gpt/figures/BERT-vs-LLMs-categories.pdf}}
				\only<4>{\includegraphics[width=\columnwidth]{../../../LLM-eval/gpt/figures/BERT-vs-LLMs-n.pdf}}
			\end{figure}
		\end{column}
	\end{columns}

	\begin{frame}{Conclusions}
\end{frame}
%	
%\begin{frame}
%	Thanks!
%	
%	\bigskip
%	
%	\hrule
%	
%	\bigskip
%	
%	\url{callaghan@mcc-berlin.net}
%	 
%	\medskip
%	
%	Twitter: @MaxCallaghan5
%	
%	\bigskip
%	
%	\begin{figure}
%	\includegraphics[width=0.1\columnwidth]{images/wellcome-logo-black.eps}
%	\end{figure}
%\end{frame}
%
